\TheTitle

### 2019-12-16 Paper1/results.tex
updated figure alignment

\begin{figure}[h!]
\centering
	\begin{subfigure}{0.3\linewidth}
		\centering
				\includegraphics[scale=0.2]{figs/Euler1DPlots5/sc100_ERho.png}
		\label{fig:referenceSolutionsub1}
	\end{subfigure}%	
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
				\includegraphics[scale=0.2]{figs/Euler1DPlots5/sc100_VarRho.png}
		\label{fig:referenceSolutionsub2}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots5/naca_mesh.png}
		\label{fig:referenceSolutionsMesh}
	\end{subfigure}
	\caption{Reference solution E$[\rho]$ and Var$[\rho]$ and the mesh close to the airfoil which is used in the computation of all presented methods.}
	\label{fig:referenceSolution}
\end{figure}

@@

\begin{figure}[h!]
\centering
\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.544]{figs/StudyQuadrature/L2_error_E[rho]_new.pdf}
		\caption{}
		\label{fig:ErrorDifferentQuadA}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.544]{figs/StudyQuadrature/L2_error_Var[rho]_new.pdf}
		\caption{}
		\label{fig:ErrorDifferentQuadB}
	\end{subfigure}
	\caption{Relative L$^2$-error with different quadrature levels for IPM in comparison with SC. The subscript denotes the moment order, the superscript denotes the number of Clenshaw-Curtis quadrature points.}
	\label{fig:ErrorDifferentQuad}
\end{figure}
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.55]{figs/errorEuler/L2_error_E[rho].pdf}
		\caption{}
		\label{fig:sub31}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.55]{figs/errorEuler/L2_error_Var[rho].pdf}
		\caption{}
		\label{fig:sub32}
	\end{subfigure}

	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.55]{figs/errorEuler/L2_error_E[rho]_sc.pdf}
		\caption{}
		\label{fig:sub33}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.55]{figs/errorEuler/L2_error_Var[rho]_sc.pdf}
		\caption{}
		\label{fig:sub34}
	\end{subfigure}
	\caption{Comparison of the relative L$^2$-error for the density for IPM related methods (first row) and of the best performing IPM method in comparison with SC (second row). All intrusive methods converge to a residual $\varepsilon=6\cdot 10^{-6}$, whereas all non-intrusive methods converge to a residual $\varepsilon=1\cdot 10^{-7}$. All computations are performed with with 5 MPI threads.}
	\label{fig:L2ErrorSolution}
\end{figure}
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots5/EulerSC5-2Res1e-6_ERho.png}
		\label{fig:sub1}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots5/sg_4_9_ERho.png}
		\label{fig:sub2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots5/osIPM4-4_ERho.png}
		\label{fig:sub1}
	\end{subfigure}\\
	\vspace{-0.35cm}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots5/EulerSC5-2Res1e-6_VarRho.png}
		\label{fig:sub1}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots5/sg_4_9_VarRho.png}
		\label{fig:sub2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots5/osIPM4-4_VarRho.png}
		\label{fig:sub1}
	\end{subfigure}
	\caption{E$[\rho]$ and Var$[\rho]$ computed with SC$^5$, SG$_4$, IPM$_4$ (from left to right). Compare to the reference solution shown in Figure \ref{fig:referenceSolution}.}
	\label{fig:ERhoVarRho5}
\end{figure}

@@

Let us finally take a look at the expectation value and variance computed with different methods. All results are depicted for a zoomed view around the airfoil. Figure~\ref{fig:ERhoVarRho5} shows the expectation value (first row) and variance (second row) computed with $5$ quadrature points for SC and $5$ moments for SG and IPM. One can observe the following
\begin{itemize}
\item All methods yield non-physical step-like profiles of the expectation value and variance along the airfoil. This effect can be observed in various settings \cite{le2004uncertainty,kusch2018filtered,poette2019contribution,barth2013non,dwight2013adaptive} and stems from Gibb's phenomena in the polynomial description of the uncertainty, either in the gPC polynomials of intrusive methods or the Lagrange polynomials used in collocation techniques. 
\item The jump position of the intrusive solution profiles capture the exact behavior more accurately.
\end{itemize}
The readosIPM results as well as the corresponding refinement levels are depicted in Figure~\ref{fig:readosIPMEVar}. One observes that the solution no longer shows the previously observed discontinuous profile and yield a satisfactory agreement with the reference solution depicted in Figure~\ref{fig:referenceSolution}. The refinement level shows that away from the airfoil, a refinement level of 0 (i.e. a truncation order of 2) suffices to yield the IPM$_9$ solution. The region with a high variance requires a refinement level of 7 (truncation order 9).
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots10/euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_ERho.png}
		\label{fig:sub1}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots10/euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_VarRho.png}
		\label{fig:sub2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots10/euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_refinementLevel.png}
		\label{fig:sub1}
	\end{subfigure}
	\caption{E$[\rho]$, Var$[\rho]$ and refinement level for readosIPM$_{2-9}$}
	\label{fig:readosIPMEVar}
\end{figure}

@@

In the following, we assume a fixed angle of attack with $\phi = 1.25$ degrees and study the effect of two sources of uncertainties, namely the farfield pressure and Mach number. The farfield pressure is ${p \sim U(100\;325,102\;325)}$ Pa and the Mach number is $Ma \sim U(0.775,0.825)$. Since this problem only has a two-dimensional uncertainty, we use a tensorized quadrature set, which in our experiments proved to be more efficient than a sparse grid quadrature. For SC, we use quadrature sets with $5^2$, $9^2$ and $17^2$ quadrature nodes and compare against SG with moments up to total degree $9$ as well as adaptive IPM with refinement retardation (with and without the One-Shot strategy). The IPM method uses moment orders ranging from $1$ to $9$ adaptively with refinement barriers $\delta_{-} = 1\cdot 10^{-4}$ and $\delta_{+} = 1\cdot 10^{-5}$. The refinement retardation allows the truncation order to have a maximal total degree of $1$ until a residual of $\varepsilon = 1.5\cdot 10^{-5}$ and then increases the truncation order by one when the residual is reduced by an amount of $5\cdot 10^{-6}$. Hence, the maximal truncation order of $9$ is reached when the residual is below $\varepsilon = 7\cdot 10^{-6}$. Again, the refinement strategy let to negative densities for SG resulting in a failure of the method.
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.5]{figs/Euler2D/L2_error_E[rho].pdf}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[scale=0.5]{figs/Euler2D/L2_error_Var[rho].pdf}
		\label{fig:sub2}
	\end{subfigure}

@@

				\includegraphics[scale=0.5]{figs/Euler2D/L2_error_E[rhoE].pdf}

@@

				\includegraphics[scale=0.5]{figs/Euler2D/L2_error_Var[rhoE].pdf}

@@

	\begin{subfigure}{0.3\linewidth}

@@

		\includegraphics[scale=0.2]{figs/Euler2D/sc50UncertainMaSigma0-025PSigma1000-0Dim2_ERho.png}

@@

		\includegraphics[scale=0.2]{figs/Euler2D/sc50UncertainMaSigma0-025PSigma1000-0Dim2_VarRho.png}

@@

		\includegraphics[scale=0.2]{figs/Euler2D/sc50UncertainMaSigma0-025PSigma1000-0Dim2_VarRho_log.png}

@@

		\includegraphics[scale=0.2]{figs/Euler2D/retadosIPM9-4MaP_4_ERho.png}

@@

		\includegraphics[scale=0.2]{figs/Euler2D/retadosIPM9-4MaP_4_VarRho.png}

@@

		\includegraphics[scale=0.2]{figs/Euler2D/retadosIPM9-4MaP_4_refinementLevel.png}

@@

	\begin{subfigure}{0.3\linewidth}

@@

		\includegraphics[scale=0.18]{figs/pipe/pipe_sc_ref_n50_E(rho).png}

@@

		\includegraphics[scale=0.18]{figs/pipe/pipe_sc_ref_n50_Var(rho).png}

@@

		\includegraphics[scale=0.18]{figs/pipe/pipe_mesh.png}

@@

		\includegraphics[scale=0.18]{figs/pipe/euler2D_pipe_adipm_n1-2_ERho.png}

@@

		\includegraphics[scale=0.18]{figs/pipe/euler2D_pipe_adipm_n1-2_VarRho.png}

@@

		\includegraphics[scale=0.18]{figs/pipe/euler2D_pipe_adipm_n1-2_refinementLevel.png}

@@

		\includegraphics[scale=0.18]{figs/pipe/euler2D_pipe_n1-4_tg1-3_ERho.png}

@@

		\includegraphics[scale=0.18]{figs/pipe/euler2D_pipe_n1-4_tg1-3_VarRho.png}

@@

		\includegraphics[scale=0.18]{figs/pipe/euler2D_pipe_n1-4_tg1-3_refinementLevel.png}

>>>>

\begin{figure}[h!]
\centering
	\begin{subfigure}{0.329\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/Euler1DPlots5/sc100_ERho.png}
		\label{fig:referenceSolutionsub1}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/Euler1DPlots5/sc100_VarRho.png}
		\label{fig:referenceSolutionsub2}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/Euler1DPlots5/naca_mesh.png}
		\label{fig:referenceSolutionsMesh}
	\end{subfigure}
	\caption{Reference solution E$[\rho]$ and Var$[\rho]$ and the mesh close to the airfoil which is used in the computation of all presented methods.}
	\label{fig:referenceSolution}
\end{figure}

@@

\begin{figure}[h!]
\centering
\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/StudyQuadrature/L2_error_E[rho]_new.pdf}
		\caption{}
		\label{fig:ErrorDifferentQuadA}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/StudyQuadrature/L2_error_Var[rho]_new.pdf}
		\caption{}
		\label{fig:ErrorDifferentQuadB}
	\end{subfigure}
	\caption{Relative L$^2$-error with different quadrature levels for IPM in comparison with SC. The subscript denotes the moment order, the superscript denotes the number of Clenshaw-Curtis quadrature points.}
	\label{fig:ErrorDifferentQuad}
\end{figure}
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/errorEuler/L2_error_E[rho].pdf}
		\caption{}
		\label{fig:sub31}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/errorEuler/L2_error_Var[rho].pdf}
		\caption{}
		\label{fig:sub32}
	\end{subfigure}

	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/errorEuler/L2_error_E[rho]_sc.pdf}
		\caption{}
		\label{fig:sub33}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/errorEuler/L2_error_Var[rho]_sc.pdf}
		\caption{}
		\label{fig:sub34}
	\end{subfigure}
	\caption{Comparison of the relative L$^2$-error for the density for IPM related methods (first row) and of the best performing IPM method in comparison with SC (second row). All intrusive methods converge to a residual $\varepsilon=6\cdot 10^{-6}$, whereas all non-intrusive methods converge to a residual $\varepsilon=1\cdot 10^{-7}$. All computations are performed with with 5 MPI threads.}
	\label{fig:L2ErrorSolution}
\end{figure}
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots5/EulerSC5-2Res1e-6_ERho.png}
		\label{fig:sub1}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots5/sg_4_9_ERho.png}
		\label{fig:sub2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots5/osIPM4-4_ERho.png}
		\label{fig:sub1}
	\end{subfigure}\\
	\vspace{-0.35cm}
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots5/EulerSC5-2Res1e-6_VarRho.png}
		\label{fig:sub1}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots5/sg_4_9_VarRho.png}
		\label{fig:sub2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots5/osIPM4-4_VarRho.png}
		\label{fig:sub1}
	\end{subfigure}
	\caption{E$[\rho]$ and Var$[\rho]$ computed with SC$^5$, SG$_4$, IPM$_4$ (from left to right). Compare to the reference solution shown in Figure \ref{fig:referenceSolution}.}
	\label{fig:ERhoVarRho5}
\end{figure}

@@

Let us finally take a look at the expectation value and variance computed with different methods. All results are depicted for a zoomed view around the airfoil. Figure~\ref{fig:ERhoVarRho5} shows the expectation value (first row) and variance (second row) computed with $5$ quadrature points for SC and $5$ moments for SG and IPM. One can observe the following
\begin{itemize}
\item All methods yield non-physical step-like profiles of the expectation value and variance along the airfoil. This effect can be observed in various settings \cite{le2004uncertainty,kusch2018filtered,poette2019contribution,barth2013non,dwight2013adaptive} and stems from Gibb's phenomena in the polynomial description of the uncertainty, either in the gPC polynomials of intrusive methods or the Lagrange polynomials used in collocation techniques. 
\item The jump position of the intrusive solution profiles capture the exact behavior more accurately.
\end{itemize}
The readosIPM results as well as the corresponding refinement levels are depicted in Figure~\ref{fig:readosIPMEVar}. One observes that the solution no longer shows the previously observed discontinuous profile and yield a satisfactory agreement with the reference solution depicted in Figure~\ref{fig:referenceSolution}. The refinement level shows that away from the airfoil, a refinement level of 0 (i.e. a truncation order of 2) suffices to yield the IPM$_9$ solution. The region with a high variance requires a refinement level of 7 (truncation order 9).
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots10/euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_ERho.png}
		\label{fig:sub1}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots10/euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_VarRho.png}
		\label{fig:sub2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.329\linewidth}
		\centering
		\includegraphics[width=\linewidth]{figs/Euler1DPlots10/euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_refinementLevel.png}
		\label{fig:sub1}
	\end{subfigure}
	\caption{E$[\rho]$, Var$[\rho]$ and refinement level for readosIPM$_{2-9}$}
	\label{fig:readosIPMEVar}
\end{figure}

@@

In the following, we assume a fixed angle of attack with $\phi = 1.25$ degrees and study the effect of two sources of uncertainties, namely the farfield pressure and Mach number. The farfield pressure is ${p \sim U(100\;325,102\;325)}$ Pa and the Mach number is $Ma \sim U(0.775,0.825)$. Since this problem only has a two-dimensional uncertainty, we use a tensorized quadrature set, which in our experiments proved to be more efficient than a sparse grid quadrature. For SC, we use quadrature sets with $5^2$, $9^2$ and $17^2$ quadrature nodes and compare against SG with moments up to total degree $9$ as well as adaptive IPM with refinement retardation (with and without the One-Shot strategy). The IPM method uses moment orders ranging from $1$ to $9$ adaptively with refinement barriers $\delta_{-} = 1\cdot 10^{-4}$ and $\delta_{+} = 1\cdot 10^{-5}$. The refinement retardation allows the truncation order to have a maximal total degree of $1$ until a residual of $\varepsilon = 1.5\cdot 10^{-5}$ and then increases the truncation order by one when the residual is reduced by an amount of $5\cdot 10^{-6}$. Hence, the maximal truncation order of $9$ is reached when the residual is below $\varepsilon = 7\cdot 10^{-6}$. Again, the refinement strategy let to negative densities for SG resulting in a failure of the method.
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/Euler2D/L2_error_E[rho].pdf}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.5\linewidth}
		\centering
				\includegraphics[width=\linewidth]{figs/Euler2D/L2_error_Var[rho].pdf}
		\label{fig:sub2}
	\end{subfigure}

@@

				\includegraphics[width=\linewidth]{figs/Euler2D/L2_error_E[rhoE].pdf}

@@

				\includegraphics[width=\linewidth]{figs/Euler2D/L2_error_Var[rhoE].pdf}

@@

	\begin{subfigure}{0.329\linewidth}

@@

		\includegraphics[width=\linewidth]{figs/Euler2D/sc50UncertainMaSigma0-025PSigma1000-0Dim2_ERho.png}

@@

		\includegraphics[width=\linewidth]{figs/Euler2D/sc50UncertainMaSigma0-025PSigma1000-0Dim2_VarRho.png}

@@

		\includegraphics[width=\linewidth]{figs/Euler2D/sc50UncertainMaSigma0-025PSigma1000-0Dim2_VarRho_log.png}

@@

		\includegraphics[width=\linewidth]{figs/Euler2D/retadosIPM9-4MaP_4_ERho.png}

@@

		\includegraphics[width=\linewidth]{figs/Euler2D/retadosIPM9-4MaP_4_VarRho.png}

@@

		\includegraphics[width=\linewidth]{figs/Euler2D/retadosIPM9-4MaP_4_refinementLevel.png}

@@

	\begin{subfigure}{0.31\linewidth}

@@

		\includegraphics[width=\linewidth]{figs/pipe/pipe_sc_ref_n50_E(rho).png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/pipe_sc_ref_n50_Var(rho).png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/pipe_mesh.png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/euler2D_pipe_adipm_n1-2_ERho.png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/euler2D_pipe_adipm_n1-2_VarRho.png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/euler2D_pipe_adipm_n1-2_refinementLevel.png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/euler2D_pipe_n1-4_tg1-3_ERho.png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/euler2D_pipe_n1-4_tg1-3_VarRho.png}

@@

		\includegraphics[width=\linewidth]{figs/pipe/euler2D_pipe_n1-4_tg1-3_refinementLevel.png}
